Testing atlantisom: visualize weight at (st)age output. How shall we interplolate this for true ages?

### 2019-05-16 TestWeightAtStage.Rmd
helps to evaluate the plotting blocks

```{r loadCCAlengthcomp, echo=TRUE, eval=FALSE}

@@

Sardine:
```{r plotCCAsardine, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Pacific_sardine")

@@

Anchovy:
```{r plotCCAanchovy, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Anchovy")

@@

Herring:
```{r plotCCAherring, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Herring")

@@

Pacific hake, 2 true ages per class:
```{r plotCCAhake, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Mesopel_M_Fish")

@@

Bocaccio rockfish, 5 true ages per age class:
```{r plotCCAbocaccio, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Bocaccio_rockfish")

@@

Yelloweye rockfish, most extreme at 12 true ages per age class:
```{r plotCCAYelloweye, eval=FALSE}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Yelloweye_rockfish")

>>>>

```{r loadCCAlengthcomp, echo=TRUE}

@@

Sardine:
```{r plotCCAsardine}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Pacific_sardine")

@@

Anchovy:
```{r plotCCAanchovy}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Anchovy")

@@

Herring:
```{r plotCCAherring}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Herring")

@@

Pacific hake, 2 true ages per class:
```{r plotCCAhake}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Mesopel_M_Fish")

@@

Bocaccio rockfish, 5 true ages per age class:
```{r plotCCAbocaccio}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Bocaccio_rockfish")

@@

Yelloweye rockfish, most extreme at 12 true ages per age class:
```{r plotCCAYelloweye}
censuswt <- length_censussurvsamp$muweight %>%
  filter(species == "Yelloweye_rockfish")
